\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-06-06 doc/paper.tex
typo
doc/paper.tex: highlight C++ comments except pseudo-codes

@@

  const double low_scale_guess_1 = low_constraint_1.get_initial_scale_guess();
  const double high_scale_guess_2 = high_constraint_2.get_initial_scale_guess();
  const double matching_scale_guess = matching.get_initial_scale_guess();
\end{numlstlisting}
Compared to the MSSM case,
the differences are that
the type of \code{high_constraint_2}
is \code{MSSMRHN_high_scale_constraint<Two_scale>} and that
\code{matching_scale_guess} has been inserted.
Due to this intermediate scale,
the initial run-up is divided into two steps,
with a matching procedure in-between:
\begin{numlstlisting}[name=MSSM_MSSMRHN_two_scale_initial_guesser.cpp]
  model_1->run_to(matching_scale_guess); // of type MSSM<Two_scale>
  matching.set_models(model_1, model_2);
  matching.match_low_to_high_scale_model();
  model_2->run_to(high_scale_guess_2);   // of type MSSMRHN<Two_scale>
\end{numlstlisting}
The high-scale constraints are applied to \code{model_2},
the higher-energy model,
and the remaining undetermined parameters are guessed:
\begin{numlstlisting}[name=MSSM_MSSMRHN_two_scale_initial_guesser.cpp]
  high_constraint_2.set_model(model_2);
  high_constraint_2.apply();
  model_2->set_Mu(1.0); model_2->set_BMu(0.0);
\end{numlstlisting}
The initial two-step run-down again involves a matching process:
\begin{numlstlisting}[name=MSSM_MSSMRHN_two_scale_initial_guesser.cpp]
  model_2->run_to(matching_scale_guess);
  matching.match_high_to_low_scale_model();
  model_1->run_to(low_scale_guess_1);
\end{numlstlisting}
At the low scale where \code{MSSM} is valid,
the code is the same as in \code{MSSM_initial_guesser}:
\begin{numlstlisting}[name=MSSM_MSSMRHN_two_scale_initial_guesser.cpp]
  model_1->solve_ewsb_tree_level();
  model_1->calculate_DRbar_parameters();
  model_1->set_thresholds(3); model_1->set_loops(2);
}
\end{numlstlisting}

@@

template<>
class MSSMcbs_low_scale_constraint<Two_scale> : public Constraint<Two_scale> {
public:
  MSSMcbs_low_scale_constraint(const MSSM_input_parameters&, const QedQcd&);
  virtual ~MSSMcbs_low_scale_constraint();
  void set_threshold_corrections(unsigned);
  ...
private:
  MSSMcbs<Two_scale>* model;
  QedQcd oneset;
  double new_g3;
  unsigned threshold_corrections;
  void calculate_DRbar_gauge_couplings();
  double calculate_alS5DRbar_over_alS5MSbar(double) const;
  double calculate_zeta_g_QCD_2(double) const;
  double calculate_zeta_g_SUSY_2(double) const;
  ...
};
\end{numlstlisting}
In line 11,
the type of \code{model} has been adapted to the new model.
In fact, this class should work even if \code{model} remained
a pointer to \code{MSSM<Two_scale>} because of inheritance.
The main additions to \code{MSSM_low_scale_constraint}
in \code{models/MSSM/} are the member functions in lines 16--18,
which evaluate the two-loop matching coefficients
from Ref.~\cite{Harlander:2005wm}.
The following member function then performs
the two-step decoupling as reported in this reference:
% MSSMcbs_two_scale_low_scale_constraint.cpp
\begin{numlstlisting}
void MSSMcbs_low_scale_constraint<Two_scale>::calculate_DRbar_gauge_couplings()
{
  ...
  double alpha_s = oneset.displayAlpha(ALPHAS);
  double alS5DRbar_over_alS5MSbar = 1;
  double zeta_g_QCD_2 = 1;
  double zeta_g_SUSY_2 = 1;
  if (model->get_thresholds()) {
    alS5DRbar_over_alS5MSbar = calculate_alS5DRbar_over_alS5MSbar(alpha_s);
    alpha_s *= alS5DRbar_over_alS5MSbar;  // alS5MSbar -> alS5DRbar
    zeta_g_QCD_2 = calculate_zeta_g_QCD_2(alpha_s);
    alpha_s /= zeta_g_QCD_2;		  // alS5DRbar -> alS6DRbar
    zeta_g_SUSY_2 = calculate_zeta_g_SUSY_2(alpha_s);
    alpha_s /= zeta_g_SUSY_2;		  // alS6DRbar -> alS6DRbarMSSM
    ...
  }
  new_g3 = Sqrt(4*Pi * alpha_s);
  ...
}
\end{numlstlisting}
Finally,
one can integrate the new boundary condition class
\code{MSSMcbs_low_scale_constraint} together with
the new model \code{MSSMcbs}
into the spectrum generator in a straightforward manner.
They should supersede
\code{MSSM_low_scale_constraint} and \code{MSSM}, respectively.
The replacement should be carried out in
those objects that depend on these classes,
i.e.\ the initial guesser:
\begin{numlstlisting}
template<>
class MSSMcbs_initial_guesser<Two_scale> : public Initial_guesser<Two_scale> {
public:
  MSSMcbs_initial_guesser(MSSMcbs<Two_scale>*,
                          const MSSM_input_parameters&,
                          const QedQcd&,
                          const MSSMcbs_low_scale_constraint<Two_scale>&,
                          const MSSM_susy_scale_constraint<Two_scale>&,
                          const MSSM_high_scale_constraint<Two_scale>&);
  ...
private:
  MSSMcbs<Two_scale>* model;
  MSSM_input_parameters input_pars;
  QedQcd oneset;
  MSSMcbs_low_scale_constraint<Two_scale> low_constraint;
  MSSM_susy_scale_constraint<Two_scale> susy_constraint;
  MSSM_high_scale_constraint<Two_scale> high_constraint;
  ...
};
\end{numlstlisting}
as well as the spectrum generator object:
% MSSMcbs_spectrum_generator.hpp
\begin{numlstlisting}
template <class T>
void MSSMcbs_spectrum_generator<T>::run(const QedQcd& oneset,
					const MSSM_input_parameters& input)
{
  ...
  MSSMcbs_initial_guesser<T> initial_guesser
    (&model, input, oneset,
     low_scale_constraint, susy_scale_constraint, high_scale_constraint);
  ...
}
\end{numlstlisting}
One can find a working realization of this example
in \code{examples/customized-betas/}.

>>>>

\begin{numlstlisting}[name=SGrun,language=C++]

@@

  const double low_scale_guess_1 = low_constraint_1.get_initial_scale_guess();
  const double high_scale_guess_2 = high_constraint_2.get_initial_scale_guess();
  const double matching_scale_guess = matching.get_initial_scale_guess();
\end{numlstlisting}
Compared to the MSSM case,
the differences are that
the type of \code{high_constraint_2}
is \code{MSSMRHN_high_scale_constraint<Two_scale>} and that
\code{matching_scale_guess} has been inserted.
Due to this intermediate scale,
the initial run-up is divided into two steps,
with a matching procedure in-between:
\begin{numlstlisting}[name=MSSM_MSSMRHN_two_scale_initial_guesser.cpp,language=C++]
  model_1->run_to(matching_scale_guess); // of type MSSM<Two_scale>
  matching.set_models(model_1, model_2);
  matching.match_low_to_high_scale_model();
  model_2->run_to(high_scale_guess_2);   // of type MSSMRHN<Two_scale>
\end{numlstlisting}
The high-scale constraints are applied to \code{model_2},
the higher-energy model,
and the remaining undetermined parameters are guessed:
\begin{numlstlisting}[name=MSSM_MSSMRHN_two_scale_initial_guesser.cpp]
  high_constraint_2.set_model(model_2);
  high_constraint_2.apply();
  model_2->set_Mu(1.0); model_2->set_BMu(0.0);
\end{numlstlisting}
The initial two-step run-down again involves a matching process:
\begin{numlstlisting}[name=MSSM_MSSMRHN_two_scale_initial_guesser.cpp]
  model_2->run_to(matching_scale_guess);
  matching.match_high_to_low_scale_model();
  model_1->run_to(low_scale_guess_1);
\end{numlstlisting}
At the low scale where \code{MSSM} is valid,
the code is the same as in \code{MSSM_initial_guesser}:
\begin{numlstlisting}[name=MSSM_MSSMRHN_two_scale_initial_guesser.cpp]
  model_1->solve_ewsb_tree_level();
  model_1->calculate_DRbar_parameters();
  model_1->set_thresholds(3); model_1->set_loops(2);
}
\end{numlstlisting}

@@

template<>
class MSSMcbs_low_scale_constraint<Two_scale> : public Constraint<Two_scale> {
public:
  MSSMcbs_low_scale_constraint(const MSSM_input_parameters&, const QedQcd&);
  virtual ~MSSMcbs_low_scale_constraint();
  void set_threshold_corrections(unsigned);
  ...
private:
  MSSMcbs<Two_scale>* model;
  QedQcd oneset;
  double new_g3;
  unsigned threshold_corrections;
  void calculate_DRbar_gauge_couplings();
  double calculate_alS5DRbar_over_alS5MSbar(double) const;
  double calculate_zeta_g_QCD_2(double) const;
  double calculate_zeta_g_SUSY_2(double) const;
  ...
};
\end{numlstlisting}
In line 11,
the type of \code{model} has been adapted to the new model.
In fact, this class should work even if \code{model} remained
a pointer to \code{MSSM<Two_scale>} because of inheritance.
The main additions to \code{MSSM_low_scale_constraint}
in \code{models/MSSM/} are the member functions in lines 16--18,
which evaluate the two-loop matching coefficients
from Ref.~\cite{Harlander:2005wm}.
The following member function then performs
the two-step decoupling as reported in this reference:
% MSSMcbs_two_scale_low_scale_constraint.cpp
\begin{numlstlisting}[language=C++]
void MSSMcbs_low_scale_constraint<Two_scale>::calculate_DRbar_gauge_couplings()
{
  ...
  double alpha_s = oneset.displayAlpha(ALPHAS);
  double alS5DRbar_over_alS5MSbar = 1;
  double zeta_g_QCD_2 = 1;
  double zeta_g_SUSY_2 = 1;
  if (model->get_thresholds()) {
    alS5DRbar_over_alS5MSbar = calculate_alS5DRbar_over_alS5MSbar(alpha_s);
    alpha_s *= alS5DRbar_over_alS5MSbar;  // alS5MSbar -> alS5DRbar
    zeta_g_QCD_2 = calculate_zeta_g_QCD_2(alpha_s);
    alpha_s /= zeta_g_QCD_2;		  // alS5DRbar -> alS6DRbar
    zeta_g_SUSY_2 = calculate_zeta_g_SUSY_2(alpha_s);
    alpha_s /= zeta_g_SUSY_2;		  // alS6DRbar -> alS6DRbarMSSM
    ...
  }
  new_g3 = Sqrt(4*Pi * alpha_s);
  ...
}
\end{numlstlisting}
Finally,
one can integrate the new boundary condition class
\code{MSSMcbs_low_scale_constraint} together with
the new model \code{MSSMcbs}
into the spectrum generator in a straightforward manner.
They should supersede
\code{MSSM_low_scale_constraint} and \code{MSSM}, respectively.
The replacement should be carried out in
those objects that depend on these classes,
i.e.\ the initial guesser:
\begin{numlstlisting}
template<>
class MSSMcbs_initial_guesser<Two_scale> : public Initial_guesser<Two_scale> {
public:
  MSSMcbs_initial_guesser(MSSMcbs<Two_scale>*,
                          const MSSM_input_parameters&,
                          const QedQcd&,
                          const MSSMcbs_low_scale_constraint<Two_scale>&,
                          const MSSM_susy_scale_constraint<Two_scale>&,
                          const MSSM_high_scale_constraint<Two_scale>&);
  ...
private:
  MSSMcbs<Two_scale>* model;
  MSSM_input_parameters input_pars;
  QedQcd oneset;
  MSSMcbs_low_scale_constraint<Two_scale> low_constraint;
  MSSM_susy_scale_constraint<Two_scale> susy_constraint;
  MSSM_high_scale_constraint<Two_scale> high_constraint;
  ...
};
\end{numlstlisting}
as well as the spectrum generator object:
% MSSMcbs_spectrum_generator.hpp
\begin{numlstlisting}
template <class T>
void MSSMcbs_spectrum_generator<T>::run(const QedQcd& oneset,
					const MSSM_input_parameters& input)
{
  ...
  MSSMcbs_initial_guesser<T> initial_guesser
    (&model, input, oneset,
     low_scale_constraint, susy_scale_constraint, high_scale_constraint);
  ...
}
\end{numlstlisting}
One can find a working realization of this example
in \code{examples/customized-betas/}.
